---
title: "CpG Observed/Expected Ratios"
author: "EL Strand"
output:
  github_document: default
  pdf_document:
    keep_tex: yes
  html_document:
    toc: yes
    toc_depth: 6
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Input is from script to calculate CpG ratios: https://github.com/emmastrand/EmmaStrand_Notebook/blob/master/_posts/2022-11-19-CpG-OE-Analysis-for-DNA-Methylation.md

This R script and model is based on Jay Dimond's: https://github.com/jldimond/Coral-CpG/blob/master/analyses/scripts/CpG_Density.R 

## Load libraries 

```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(mixtools)
library(fitdistrplus)
```

## Load data 

```{r}
cpg_anno <- read.delim("Dec-July-2019-analysis/output/WGBS/Mcap_cpg_anno.txt", header=FALSE) %>%
  rename(Gene = V1) %>% rename(CpG_ratio = V2)

set.seed(101)
```

## Choosing cut-offs 

```{r}
range(cpg_anno$CpG_ratio)
hist(cpg_anno$CpG_ratio)

cpg_anno <- cpg_anno %>% 
  filter(CpG_ratio >= 0.001) %>% # setting minimum
  filter(CpG_ratio <= 1.5) # setting maximum 

range(cpg_anno$CpG_ratio)
```

## Fitting mixture model with mixtools normalmixEM

https://dozenoaks.twelvetreeslab.co.uk/2019/06/mixture-models/

`normalmixEM` functions is telling it to find two gaussians in the observations

```{r}
mixmodel <- normalmixEM(cpg_anno$CpG_ratio, k = 2)

plot(mixmodel, which = 2)
```

### Plotting the above model

```{r}
cpg_anno %>% 
  ggplot(., aes(x=CpG_ratio)) + theme_classic() + 
  geom_histogram(binwidth=0.1, fill = "white", color="darkgrey", alpha=0.9) + 
  ylab("Number of genes") + xlab("CpG Observed/Expected") +
  mapply(
    function(mean, sd, lambda, n, binwidth) {
      stat_function(
        fun = function(x) {
          (dnorm(x, mean = mean, sd = sd)) * n * binwidth * lambda
        }
      )
    },
    mean = mixmodel[["mu"]], #mean
    sd = mixmodel[["sigma"]], #standard deviation
    lambda = mixmodel[["lambda"]], #amplitude
    n = length(cpg_anno$CpG_ratio), #sample size
    binwidth = 0.1 #binwidth used for histogram; needs to match the above binwidth 
  )
```

## Finds intersection point of two component model

```{r}
intersect <- function(m1, s1, m2, s2, prop1, prop2){
  
  B <- (m1/s1^2 - m2/s2^2)
  A <- 0.5*(1/s2^2 - 1/s1^2)
  C <- 0.5*(m2^2/s2^2 - m1^2/s1^2) - log((s1/s2)*(prop2/prop1))
  
  (-B + c(1,-1)*sqrt(B^2 - 4*A*C))/(2*A)
}

mixmodel[["mu"]] #means
mixmodel[["sigma"]] #standard deviations
mixmodel[["lambda"]] #amplitudes

intersect_pt <- intersect(mixmodel[["mu"]][1], mixmodel[["sigma"]][1], 
                          mixmodel[["mu"]][2], mixmodel[["sigma"]][2], 
                          mixmodel[["lambda"]][1], mixmodel[["lambda"]][2])
```

## Tests fit of single component model

```{r}
fitdistr(cpg_anno$CpG_ratio, "normal")
```

## Weakly and heavily methylated genes 

```{r}
cpg_anno <- cpg_anno %>%
  mutate(status = if_else(CpG_ratio >= intersect_pt[2], "weakly", "heavily"))

nrow(cpg_anno) # 24,065
nrow(cpg_anno[cpg_anno$status == "weakly",]) # 19,440
nrow(cpg_anno[cpg_anno$status == "heavily",])# 4,625
```