---
title: "ITS2 Analysis of KBAY Bleaching Pairs"
author: "EL Strand"
output:
  github_document: default
  pdf_document:
    keep_tex: yes
  html_document:
    toc: yes
    toc_depth: 6
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ITS2 Analysis 

Complete the following workflow in terminal using SymPortal before starting this R script: [Emma Strand Notebook post](https://github.com/emmastrand/EmmaStrand_Notebook/blob/master/_posts/2022-01-14-KBay-Bleaching-Pairs-ITS2-Analysis-Pipeline.md#Troubleshooting).
## Load libraries 

```{r}
#install_github("pmartinezarbizu/pairwiseAdonis/pairwiseAdonis")
p1 <- c("plyr", "dplyr", "tidyverse", "vegan", "BiocManager", "ggpubr", "janitor", "funrar", "AMR", "ggbiplot", "stats",
        "devtools", "pairwiseAdonis", "lubridate", "ggh4x", "ggfortify", "naniar")
p2 <- c("phyloseq", "ANCOMBC", "DESeq2", "ComplexHeatmap","microbiomeMarker")
load_package <- function(p) {
  if (!requireNamespace(p, quietly = TRUE)) {
    ifelse(p %in% p1, 
           install.packages(p, repos = "http://cran.us.r-project.org/"), 
           BiocManager::install(p))
  }
  library(p, character.only = TRUE, quietly = TRUE)
}
invisible(lapply(c(p1,p2), load_package))
```


#### Read in metadata file 

This file was created during the above workflow. Sample ID is the ID given during sequencing. ColonyID is the ID given during field work and what the coral is tagged as. 

```{r}
metadata <- read.csv("Dec-July-2019-analysis/output/ITS2/metadata/metadata.csv", header = TRUE)
```


## Type Profile Level

#### Read in Type Profile dataframes. SymPortal outputs both absolute and relative abundance data as text files. 

**Relative abundance** 

```{r}
relative.abundance.raw <- read.delim("Dec-July-2019-analysis/output/ITS2/processed_data/20220119T075742/its2_type_profiles/5_BleachingPairs_analysis_20220119T075742.profiles.relative.abund_and_meta.txt", sep = "\t", dec = ".", na.strings=c("","NA"))

relative.abundance <- relative.abundance.raw %>% 
  dplyr::rename(Sample.ID = X) %>% 
  dplyr::rename(`C31/C17d-C21-C21ac` = X6) %>%
  dplyr::rename(`C31-C17d-C21-C31.1-C31a-C17e` = X7) %>% 
  dplyr::rename(`C31-C17d-C31.1-C21-C31a-1373` = X8) %>% 
  dplyr::rename(`D1-D4-D6-D1ab` = X9) %>%
  filter(!is.na(Sample.ID))

relative.abundance <- full_join(relative.abundance, metadata, by = "Sample.ID") %>%
  gather(Type.Profile, Relative.Abundance, 3:6)

relative.abundance$Relative.Abundance <- as.numeric(relative.abundance$Relative.Abundance)
relative.abundance$ColonyID <- as.character(relative.abundance$ColonyID)

relative.abundance <- relative.abundance %>% unite(Group, ColonyID, Timepoint, sep = " ", remove = FALSE)
relative.abundance <- relative.abundance %>% unite(Big.Group, Bleach, Group, sep = " ", remove = FALSE)

# mean rel ab by group
relative.abundance2 <- relative.abundance %>%
  group_by(Timepoint, Bleach, Type.Profile) %>%
  mutate(mean_relabund = mean(Relative.Abundance))
```

```{r}
bl1 <- relative.abundance %>% 
  replace_with_na_all(condition = ~.x == 0.000000000) %>%
  ggplot(., aes(x = ColonyID, y = Type.Profile)) + 
  geom_tile(aes(fill = Relative.Abundance), color = "black") +
  scale_fill_distiller(palette = "YlGn", na.value = "white", 
                       direction=100, labels = scales::label_percent(scale=100),
                       limits = c(min(relative.abundance$Relative.Abundance), max(relative.abundance$Relative.Abundance))) + 
  theme_classic() +
  theme(axis.text.x.bottom = element_text(angle = 60, hjust=1),
        axis.text.y = element_text(colour = 'black', size = 10, face = 'italic'),) + 
  facet_grid(Timepoint~Bleach, scales = "free",) +
  labs(x="Colony ID", fill="Relative Abundance", y="Clade") 

ggsave(file="Dec-July-2019-analysis/output/ITS2/figures/ITS2-RelAb-Spp.png", bl1, width = 8, height = 4, units = c("in"))
```



**Absolute abundance** 

```{r}
absolute.abundance.raw <- read.delim("~/MyProjects/HI_Bleaching_Timeseries/Dec-July-2019-analysis/output/ITS2/processed_data/20220119T075742/its2_type_profiles/5_BleachingPairs_analysis_20220119T075742.profiles.absolute.abund_and_meta.txt", header = TRUE, sep = "\t", dec = ".", na.strings=c("","NA"))

absolute.abundance <- absolute.abundance.raw %>% 
  dplyr::rename(Sample.ID = X) %>% dplyr::rename(`C31/C17d-C21-C21ac` = X6) %>%
  dplyr::rename(`C31-C17d-C21-C31.1-C31a-C17e` = X7) %>% 
  dplyr::rename(`C31-C17d-C31.1-C21-C31a-1373` = X8) %>% 
  dplyr::rename(`D1-D4-D6-D1ab` = X9) %>%
  filter(!is.na(Sample.ID))
```

#### Plotting 

**Relative abundance** 

Plotting altgoether. 

```{r}
#cols <- c("deepskyblue", "darkblue", "cyan2", "darkmagenta")

ggplot(data = relative.abundance, mapping = aes(x = Timepoint, y = Relative.Abundance, fill = Type.Profile)) +
    geom_bar(position="fill", stat="identity") +
    ylab("Relative Abundance") +
    facet_grid(~Bleach) +
    #scale_fill_manual(values = cols) +
    labs(x = "Phenotype") +
    theme_classic()+
    theme(axis.text.x = element_text(size=rel(1), vjust = 0.3, hjust = 0.3)) +
    theme(legend.title = element_text(size = 6), 
               legend.text = element_text(size = 4))

#ggsave("~/MyProjects/HI_Bleaching_Timeseries/Dec-July-2019-analysis/output/ITS2/figures/rel.ab.blch.status.pdf")

ggplot(data = relative.abundance, mapping = aes(x = Big.Group, y = Relative.Abundance, fill = Type.Profile)) +
    geom_bar(position="fill", stat="identity") +
    ylab("Relative Abundance") +
    #facet_grid(~Bleach) +
    #scale_fill_manual(values = cols) +
    labs(x = "Colony ID", title = "All samples by ID #. Timepoints next to each other") +
    theme_classic()+
    theme(axis.text.x = element_text(size=rel(1), angle = 90, vjust = 0.3, hjust = 0.3)) +
    theme(legend.title = element_text(size = 6), 
               legend.text = element_text(size = 4))

#ggsave("~/MyProjects/HI_Bleaching_Timeseries/Dec-July-2019-analysis/output/ITS2/figures/rel.ab.blch.all.pdf")

ggplot(relative.abundance, aes(x = ColonyID, y = Type.Profile)) + 
  geom_point(aes(size = Relative.Abundance, fill = Type.Profile), alpha = 0.75, shape = 21) + 
  scale_size_continuous(limits = c(0.000001, 100), range = c(1,17), breaks = c(1,25,50,100)) + 
  facet_nested_wrap(facets =  vars(Bleach, Timepoint), nest_line = TRUE) + 
  labs(x = "", y = "", size = "Relative Abundance (%)", fill = "")  + 
  theme(legend.key=element_blank(), 
        #strip.background = element_rect(color="black", fill="white", size=0.5, linetype="solid"),
        strip.background = element_blank(),
        ggh4x.facet.nestline = element_line(colour = "black"),
        #strip.text = element_markdown(size = 12, lineheight = 1.1),
        axis.text.x = element_text(colour = "black", size = 12, angle = 90, vjust = 0.3, hjust = 1), 
        axis.text.y = element_text(colour = "black", size = 11), 
        legend.text = element_text(size = 10, face ="bold", colour ="black"), 
        legend.title = element_text(size = 12, face = "bold"), 
        panel.background = element_blank(), panel.border = element_rect(colour = "black", fill = NA, size = 0.5), 
        legend.position = "bottom")

#ggsave("~/MyProjects/HI_Bleaching_Timeseries/Dec-July-2019-analysis/output/ITS2/figures/rel.ab.bubble.pdf")

relative.abundance %>% subset(Bleach=="Bleach") %>%
  ggplot(., aes(x = ColonyID, y = Type.Profile)) + 
  geom_tile(aes(fill = Relative.Abundance), color = "grey") +
  facet_nested_wrap(facets =  vars(Bleach, Timepoint), nest_line = TRUE) + 
  scale_fill_distiller(palette = "Purples", direction=100, labels = scales::label_percent(scale=100)) + 
  theme_classic() +
  theme(axis.text.x.bottom = element_text(angle = 60),
        axis.text.y = element_text(colour = 'black', size = 10, face = 'italic')) + 
  labs(x="Colony ID", fill="Relative Abundance", y="Clade") 

#ggsave("Dec-July-2019-analysis/output/ITS2/figures/relab-heatmap-Bleach.pdf", width = 7, height = 3, units = c("in"))

relative.abundance %>% subset(Bleach=="Non-bleach") %>%
  ggplot(., aes(x = ColonyID, y = Type.Profile)) + 
  geom_tile(aes(fill = Relative.Abundance), color = "grey") +
  facet_nested_wrap(facets =  vars(Bleach, Timepoint), nest_line = TRUE) + 
  scale_fill_distiller(palette = "Purples", direction=100, labels = scales::label_percent(scale=100)) + 
  theme_classic() +
  theme(axis.text.x.bottom = element_text(angle = 60),
        axis.text.y = element_text(colour = 'black', size = 10, face = 'italic')) + 
  labs(x="Colony ID", fill="Relative Abundance", y="Clade") 

#ggsave("Dec-July-2019-analysis/output/ITS2/figures/relab-heatmap-nonBleach.pdf", width = 7, height = 3, units = c("in"))
```

Splitting the data frame to plot separately.  

```{r}
bleach <- relative.abundance %>% subset(Bleach == "Bleach")
non.bleach <- relative.abundance %>% subset(Bleach == "Non-bleach")

bleach.plot <- ggplot(data = bleach, mapping = aes(x = Group, y = Relative.Abundance, fill = Type.Profile)) +
    geom_bar(position="fill", stat="identity") +
    ylab("Relative Abundance") +
    #facet_grid(~Bleach) +
    #scale_fill_manual(values = cols) +
    labs(x = "Colony ID", title = "Bleached Phenotype") +
    theme_classic()+
    theme(axis.text.x = element_text(size=rel(1), angle = 90, vjust = 0.3, hjust = 0.3)) +
    theme(legend.title = element_text(size = 6), 
               legend.text = element_text(size = 4))

nonbleach.plot <- ggplot(data = non.bleach, mapping = aes(x = Group, y = Relative.Abundance, fill = Type.Profile)) +
    geom_bar(position="fill", stat="identity") +
    ylab("Relative Abundance") +
    #facet_grid(~Bleach) +
    #scale_fill_manual(values = cols) +
    labs(x = "Colony ID", title = "Tolerant (Non-Bleached) Phenotype") +
    theme_classic()+
    theme(axis.text.x = element_text(size=rel(1), angle = 90, vjust = 0.3, hjust = 0.3)) +
    theme(legend.title = element_text(size = 6), 
               legend.text = element_text(size = 4))

phenotype <- ggarrange(bleach.plot, nonbleach.plot, ncol = 1, nrow = 2)
phenotype

ggsave("~/MyProjects/HI_Bleaching_Timeseries/Dec-July-2019-analysis/output/ITS2/figures/rel.ab.ind.stitched.pdf", phenotype, width = 8, height = 12, units = c("in"))
```


## Sequence ID Level 

I read this dataframe in to check if WSH123 had any sequences at all. It did not. 

```{r}
seq.rel.abundance.raw <- read.delim("~/MyProjects/HI_Bleaching_Timeseries/data/ITS2/processed_data/20220119T075742/post_med_seqs/5_BleachingPairs_analysis_20220119T075742.seqs.relative.abund_and_meta.txt", sep = "\t", dec = ".", na.strings=c("","NA"))
```

## PERMANOVA 

Didn't scale because these are already relative abundance values and therefore scaled. 

```{r}
# all 
rel.matrix <- relative.abundance %>% select(Sample.ID, Type.Profile, Relative.Abundance) %>% spread(Type.Profile, Relative.Abundance)
rownames(rel.matrix) <- rel.matrix[,1]
rel.matrix <- rel.matrix %>% select(-Sample.ID)

rel.meta <- relative.abundance %>% 
  select(Sample.ID, ColonyID, Timepoint, Bleach) %>%
  distinct() %>%
  arrange(Sample.ID)

adonis2(rel.matrix ~ Timepoint*Bleach, data = rel.meta, method='eu')

# only single portion
rel.matrix.bleach <- relative.abundance %>% #subset(Bleach=="Non-bleach") %>% 
  subset(Timepoint == "2019-12-04") %>%
  select(Sample.ID, Type.Profile, Relative.Abundance) %>% spread(Type.Profile, Relative.Abundance)
rownames(rel.matrix.bleach) <- rel.matrix.bleach[,1]
rel.matrix.bleach <- rel.matrix.bleach %>% select(-Sample.ID)

rel.meta.bleach <- relative.abundance %>% #subset(Bleach=="Non-bleach") %>% 
  subset(Timepoint == "2019-12-04") %>%
  select(Sample.ID, ColonyID, Timepoint, Bleach) %>%
  distinct() %>%
  arrange(Sample.ID)

adonis2(rel.matrix.bleach ~ Bleach, data = rel.meta.bleach, method='eu')
```

Number of raw counts

```{r}
counts <- read.delim("Dec-July-2019-analysis/output/ITS2/processed_data/20220119T075742/its2_type_profiles/5_BleachingPairs_analysis_20220119T075742.profiles.absolute.abund_only.txt", sep = "\t", header = T)

count1=sum(counts$X6)
count2=sum(counts$X7)
count3=sum(counts$X8)
count4=sum(counts$X9)

count1+count2+count3+count4
```

## PCA 

```{r}
relative.abundance.pca.df <- relative.abundance %>%
  select(Sample.ID, Timepoint, Bleach, Type.Profile, Relative.Abundance)

rel.data <- relative.abundance.pca.df %>% 
  select(Sample.ID, Type.Profile, Relative.Abundance) %>%
  spread(Type.Profile, Relative.Abundance)
rownames(rel.data) <- rel.data[,1] #making the fragment ids the row names 
rel.data <- rel.data %>% select(-Sample.ID)

rel.data.results <- prcomp(rel.data, retx=TRUE, center=TRUE) # principal components analysis on sym data
summary(rel.data.results)
screeplot(rel.data.results, type = "line", main = "Scree plot")

relab_pca_output <- rel.data.results$x %>% as.data.frame
relab_pca_output$Sample.ID <- rownames(relab_pca_output)
relab_pca_output <- full_join(relab_pca_output, relative.abundance.pca.df, by = "Sample.ID") # replace this meta df for both species 

pca_save <- 
  relab_pca_output %>%
  ggplot(., aes(x=PC1,y=PC2, color=Bleach, shape=Timepoint)) + 
  #stat_ellipse(aes(color = Timepoint), alpha = 0.4, lwd = 0.5) +
  geom_point(size = 3, alpha = .1, stroke = 0) +
    guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  theme_classic() +
  theme(legend.position = "right") 
  #geom_polygon(data = hulls_mcap_pca, aes(lty = Host_species), lwd = 0.8) +
 # scale_color_manual(palette("Blues")) + 
  #labs(x=paste0("PC1: ",round(var_explained[1]*100,1),"%"),
     #  y=paste0("PC2: ",round(var_explained[2]*100,1),"%"))

biplot.pca <- ggbiplot(relab_pca_output, choices = 1:2, pc.biplot = TRUE, labels = row.names(pca.out), 
         labels.size = 3, alpha = 1, var.axes = TRUE, varname.size = 3,
         varname.adjust = -1, varname.abbrev = FALSE) + 
  theme_classic()
```



