---
title: "16S.Rmd"
author: "Emma Strand"
date: "2/4/2022"
output:
  html_document:
    toc: yes
    toc_depth: 6
    toc_float: yes
  pdf_document:
    keep_tex: yes
editor_options: 
  chunk_output_type: console
---

Set up workspace, set options, and load required packages. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r, warning=FALSE, message=FALSE}
## install packages if you dont already have them in your library
if ("tidyverse" %in% rownames(installed.packages()) == 'FALSE') install.packages('tidyverse') 
if ("ggplot2" %in% rownames(installed.packages()) == 'FALSE') install.packages('ggplot2') 
if ("cowplot" %in% rownames(installed.packages()) == 'FALSE') install.packages('cowplot') 
if ("janitor" %in% rownames(installed.packages()) == 'FALSE') install.packages('janitor') 
if ("car" %in% rownames(installed.packages()) == 'FALSE') install.packages('car') 
if ("phyloseq" %in% rownames(installed.packages()) == 'FALSE') BiocManager::install('phyloseq') 
if ("stringr" %in% rownames(installed.packages()) == 'FALSE') BiocManager::install('stringr')
if ("ape" %in% rownames(installed.packages()) == 'FALSE') BiocManager::install('ape') 
if ("DESeq2" %in% rownames(installed.packages()) == 'FALSE') BiocManager::install('DESeq2') 
if ("microViz" %in% rownames(installed.packages()) == 'FALSE') devtools::install_github("david-barnett/microViz@0.9.0") 
if ("vegan" %in% rownames(installed.packages()) == 'FALSE') install.packages('vegan') 
#load packages
library("ggplot2")
library('cowplot')
library("tidyverse")
library("janitor")
library("car")
library("phyloseq")
library("stringr")
library("ape")
library("DESeq2")
library("microViz")
library("vegan")
library(plyr)
library(dplyr)
library(stringr)
```

# Load Data 

Import OTU and taxonomy table. 

```{r}
otu.full<-read.table("~/MyProjects/HI_Bleaching_Timeseries/data/16S/mothur_output/kbay.opti_mcc.shared", sep='\t', header=TRUE)
taxonomy.raw<-read.table("~/MyProjects/HI_Bleaching_Timeseries/data/16S/mothur_output/kbay.taxonomy", sep='\t', header=TRUE)

## used write csv to be able to open this file in excel and edit the columns 
# write.csv(taxonomy.raw,"~/MyProjects/HI_Bleaching_Timeseries/data/16S/mothur_output/kbay.taxonomy.csv", row.names = FALSE)
## Within excel, used text to column function to separate the taxonomy column into 6

taxonomy<-read.csv("~/MyProjects/HI_Bleaching_Timeseries/data/16S/mothur_output/kbay.taxonomy.csv", sep=',', header=TRUE)
```

Load sample information.
```{r}
metadata.raw <- read.table("~/MyProjects/HI_Bleaching_Timeseries/data/16S/metadata/metadata.txt", sep='\t', header=FALSE) %>%
  dplyr::rename(sample = V1) %>% dplyr::rename(colony.id = V2) %>% dplyr::rename(timepoint = V3) %>% select(-V4,-V5,-V6) %>% dplyr::rename(bleach = V7) %>%
  unite(group, timepoint, bleach, remove = FALSE, sep = " ")

metadata <- metadata.raw
rownames(metadata) <- metadata$sample

metadata <- metadata %>% select(!sample)
```

Set default plot theme.  

```{r}
theme_set(theme_bw())
```

# RELATIVE ABUNDANCE 

```{r}
otu.rel <- otu.full %>% select(-label, -numOtus) %>% dplyr::rename(sample = Group)
rownames(otu.rel) <- otu.rel$sample
otu.rel <- otu.rel %>% select(-sample)

Rel.OTU.Data <- otu.rel/rowSums(otu.rel) # calculate the Relative Abundance
N <- rowSums(Rel.OTU.Data) # calculate row sums of the relative abundances, should sum to 1
N #Display Row Sums, should all be 1

ggplot(data = relative.abundance, mapping = aes(x = Timepoint, y = Relative.Abundance, fill = Type.Profile)) +
    geom_bar(position="fill", stat="identity") +
    ylab("Relative Abundance") +
    facet_grid(~Bleach) +
    #scale_fill_manual(values = cols) +
    labs(x = "Phenotype") +
    theme_classic()+
    theme(axis.text.x = element_text(size=rel(1), vjust = 0.3, hjust = 0.3)) +
    theme(legend.title = element_text(size = 6), 
               legend.text = element_text(size = 4))
```


# PHYLOSEQ 
# Tree and heatmap 

Prepare the matrix to be all numeric with taxa in rows.  
```{r}
otu.full <- otu.full %>% select(-label,-numOtus)
rownames(otu.full) <- otu.full$Group
otu.full <- otu.full %>% select(-Group)
otu.full <- t(otu.full)
```

Prepare the taxonomy table.  
```{r}
## taxonomy <- str_split_fixed(taxonomy$Taxonomy, ";", 6)
## the above function could be used later to split instead of the excel short cut, come back to this 

rownames(taxonomy) <- taxonomy$OTU
 
taxonomy <- taxonomy %>% select(-Size, -OTU) %>%
   mutate_all(funs(str_replace_all(., "\\([^\\)]+\\)", ""))) %>% # remove the certainty % values in parentheses for each taxa 
  dplyr::rename(Domain = Taxonomy) %>% dplyr::rename(Phylum = X) %>% dplyr::rename(Class = X.1) %>% dplyr::rename(Order = X.2) %>%
  dplyr::rename(Family = X.3) %>% dplyr::rename(Genus = X.4)

taxonomy <- as.matrix(taxonomy)
```

Combine the OTU and taxonomic information. 
```{r}
OTU_full = otu_table(otu.full, taxa_are_rows = TRUE)
TAX = tax_table(taxonomy)
OTU_full
```

Load into phyloseq.  
```{r}
physeq = phyloseq(OTU_full, TAX)
physeq
```

Plot an abundance table at the different taxonomic levels.    

```{r}
plot_bar(physeq, fill = "Domain") + theme(legend.position="bottom")
plot_bar(physeq, fill = "Phylum") + theme(legend.position="bottom")
plot_bar(physeq, fill = "Class") + theme(legend.position="bottom")
plot_bar(physeq, fill = "Order") + theme(legend.position="bottom")
plot_bar(physeq, fill = "Family") + theme(legend.position="bottom")
plot_bar(physeq, fill = "Genus") + theme(legend.position="bottom")
```

Plot a tree of OTU's.  
```{r}
random_tree = rtree(ntaxa(physeq), rooted=TRUE, tip.label=taxa_names(physeq))
plot(random_tree)
```

Generate sample information.  
```{r}
sampledata = sample_data(data.frame(
  timepoint = metadata$timepoint,
  bleach = metadata$bleach, 
  colony.id = metadata$colony.id,
  group = metadata$group,
  row.names=sample_names(physeq),
  stringsAsFactors=FALSE
))
sampledata
```

Merge the tree, sample information, and OTU table.  
```{r}
physeq1 = merge_phyloseq(physeq, sampledata, random_tree)
physeq1
```

Now rebuild phyloseq.  
```{r}
physeq2 = phyloseq(OTU_full, TAX, sampledata, random_tree)
physeq2
```

Check that they are identical. Should return TRUE.  
```{r}
identical(physeq1, physeq2)
```

## Filter out samples here if needed

Plot abundance by category. 

```{r}
plot_bar(physeq, fill = "Class") + theme(legend.position="bottom")
plot_bar(physeq1, fill="Class", facet_grid=~group) + theme(legend.position="bottom")
```

Now build a tree with the combined data.  
```{r}
plot_tree(physeq1, color="timepoint", label.tips="taxa_names", ladderize="left", plot.margin=0.3)
plot_tree(physeq1, color="bleach", label.tips="taxa_names", ladderize="left", plot.margin=0.3)
```

Plot a heatmap.  

```{r}
plot_heatmap(physeq1, "NMDS", "bray", "timepoint", "Family", low="#66CCFF", high="#000033", na.value="white")
plot_heatmap(physeq1, "NMDS", "bray", "bleach", "Family", low="#66CCFF", high="#000033", na.value="white")
```

# NMDS 

```{r}
GP1 = physeq1
GP1
```

Transform to even sampling depth.  
```{r}
GP1 = transform_sample_counts(GP1, function(x) 1E6 * x/sum(x))
```

View ordination by OTU.  
```{r}
GP.ord <- ordinate(GP1, "NMDS", "bray")
p1 = plot_ordination(GP1, GP.ord, type="taxa", color="Class", title="taxa")
```

View faceted by Phylum.  
```{r}
p1 + facet_wrap(~Class, 3) + theme(legend.position="none")
```

Plot with samples now.  
```{r}
p2 = plot_ordination(GP1, GP.ord, type="samples", color="group", shape="group") + geom_point(size=3) + 
  ggtitle("16S communities") + stat_ellipse() + 
  scale_color_manual(values = c("green3", "darkgreen", "lightblue", "darkblue")) 
#+ geom_polygon(aes(fill=timepoint))


```

Plot OTU and sample plots together.  
```{r}
p3 = plot_ordination(GP1, GP.ord, type="split", color="Phylum", label="timepoint", title="split") 
p3
```

Now view through different ordination methods. 

```{r}
dist = "bray"
ord_meths = c("DCA", "CCA", "RDA", "DPCoA", "NMDS", "MDS", "PCoA")
plist = plyr::llply(as.list(ord_meths), function(i, physeq, dist){
        ordi = ordinate(physeq, method=i, distance=dist)
        plot_ordination(physeq, ordi, "samples", color="timepoint")
}, GP1, dist)
names(plist) <- ord_meths
pdataframe = plyr::ldply(plist, function(x){
    df = x$data[, 1:2]
    colnames(df) = c("Axis_1", "Axis_2")
    return(cbind(df, x$data))
})
names(pdataframe)[1] = "method"
p = ggplot(pdataframe, aes(Axis_1, Axis_2, color=timepoint, fill=timepoint))
p = p + geom_point(size=4) + geom_polygon()
p = p + facet_wrap(~method, scales="free")
#p = p + scale_fill_brewer(type="qual", palette="Set1")
#p = p + scale_colour_brewer(type="qual", palette="Set1")
p
```

Display NMDS, the method we will be using.  
```{r}
p = plist[[5]] 
p = p + geom_point(size=2) + stat_ellipse() 
p
```

Conduct a permanova in the vegan package.  

```{r}
metadata <- as(sample_data(GP1), "data.frame")
adonis(phyloseq::distance(GP1, method="bray") ~ timepoint*bleach,
       data = metadata)
```

# Networks  

Remove NA's. 
```{r}
GP3f = physeq1
```

Plot network.  
```{r}
plot_net(GP3f, maxdist = 1, point_label = "bleach", color = "timepoint")
```

Plot network.  
```{r}
igF <- make_network(GP3f, max.dist=1)
plot_network(igF, GP3f, color="timepoint", label=NULL)
```


